### 2017-01-08 2017mergingmerges/section/A1-Combinators.tex
a few combinators. just for fun

@@

>>>>

\begin{code}
takes n = process
     ins: lens vals
    outs: olens ovals
    heap: {count, takecount, ix, val}
   label: init0
  blocks: init0 = pull lens count lens0
          lens0 = jump lens1
                [ ix = 0
                , takecount = min count n ]
          lens1 = push olens takecount take0
          take0 = case (ix < takecount) take1 drop0
          take1 = pull vals val take2
          take2 = push ovals val take0[ix = ix + 1]
          drop0 = case (ix < count) drop1 init0
          drop1 = pull vals val drop0[ix = ix + 1]
\end{code}

@@

\begin{code}
apps = process
     ins: Alens Avals Blens Bvals
    outs: olens ovals
    heap: {Alen, Blen, val}
   label: init0
  blocks: init0 = pull Alens Alen init1
          init1 = pull Blens Blen init2
          init2 = push olens  (Alen + Blen) copyA0
          copyA0 = case (Alen > 0) copyA1 copyB0
          copyA1 = pull Avals val copyA2
          copyA2 = push ovals val copyA0[Alen = Alen - 1]
          copyB0 = case (Blen > 0) copyB1 init0
          copyB1 = pull Bvals val copyB2
          copyB2 = push ovals val copyB0[Blen = Blen - 1]
\end{code}
